---
title: "R Notebook"
output: html_notebook
---

# Dependencies
```{r}
# data wrangling
library(tidyverse)

# spatial data wrangling
library(sf)

# data visualisation
library(viridis) 

# format data visualisations
library(ggthemes)
library(patchwork)
library(showtext)
library(scales)
library(classInt)
library(ggtext)

# create maps
library(leaflet)
library(tmap)
library(mapdeck)
library(patchwork)
```

# Setting theme

Set font style
```{r}
# clean workspace
rm(list=ls())
# load font
font_add_google("Roboto Condensed", "robotocondensed")
# automatically use showtext to render text
showtext_auto()
```

Theme for maps
```{r}
theme_map <- function(...) {
  theme_tufte() +
  theme(
    text = element_text(family = "robotocondensed", size = 20),
    # remove all axes
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
    )
}
```

Have to add a category to the number of moves column - a count < 5 - probably after the section *classify data*


# Argentina

## Data

### mobility data
```{r}
## need to read this in 4 separate times - 202

# 2020 out
df20_b <- readRDS("/Volumes/RECAST/data/outputs/argentina/movements/2020_04_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "AR") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')

# 2022 out
df22_b <- readRDS("/Volumes/RECAST/data/outputs/argentina/movements/2022_03_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "AR") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')
```

### boundary data
```{r}
adm_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_ARG_shp/gadm41_ARG_2.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')

region_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_ARG_shp/gadm41_ARG_0.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')
```

## Data wrangling
```{r}
area_names <- c("José C. Paz", "San Miguel", "Morón", "Capital Federal", "Esteban Echeverría", "Florencio Varela")

# filter for the area names which are within Buenos Aires
df20_out <- df20_b %>% dplyr::filter(start_polygon_name %in% area_names)
df22_out <- df22_b %>% dplyr::filter(start_polygon_name %in% area_names)

df20_out$start_polygon_name <- 'Buenos Aires'
df22_out$start_polygon_name <- 'Buenos Aires'

df20_out <- df20_out %>% filter(!end_polygon_name %in% area_names)
df22_out <- df22_out %>% filter(!end_polygon_name %in% area_names)
```

### Define distance
```{r}
df20_out <- df20_out %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

df22_out <- df22_out %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

```

### preserve a unique geometry
```{r}
df20_out <- df20_out %>%
  group_by(end_polygon_name) %>%
  mutate(geometry = st_union(geometry)) %>%
  ungroup()

df22_out <- df22_out %>%
  group_by(end_polygon_name) %>%
  mutate(geometry = st_union(geometry)) %>%
  ungroup()
```

### Sum of flows
```{r}
outflows_df_20 <- df20_out %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, end_polygon_name, geometry, distance_class) %>% 
  dplyr::summarise(
    sum_outflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 

outflows_df_22 <- df22_out %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, end_polygon_name, geometry, distance_class) %>% 
  dplyr::summarise(
    sum_outflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 
```

### Check alignment between data frames
```{r}
p <- ggplot() + 
  geom_sf(data = adm_shp,
          color = "gray60", 
          size = 0.1) 

last_plot()
```

```{r}
p <- p +
  geom_point(data = outflows_df_20,
    aes(geometry = geometry),
    stat = "sf_coordinates"
  ) 
last_plot()
```

### Add year
```{r}
outflows_df_20$year <- '2020'
outflows_df_22$year <- '2022'
```

### Bind outflows
```{r}
outflows_df <- rbind(outflows_df_20, outflows_df_22)
```

### Join flows to polygons
```{r}
mob_indicators_1 <- st_join(adm_shp, outflows_df)
```

### classify data into quantiles
```{r}
mob_indicators_1$new_jenk_class <- classify_intervals(mob_indicators_1$sum_outflow, n = 5, style = "quantile", factor = TRUE)

outflow_labels_1 <- levels(mob_indicators_1$new_jenk_class)
outflow_labels_1 <- gsub("^.|.$", "",  outflow_labels_1)
outflow_labels_1 <- gsub("\\.[0-9]+", "",  outflow_labels_1)
outflow_labels_1 <- gsub("\\,", "-",  outflow_labels_1)
levels(mob_indicators_1$new_jenk_class) <- outflow_labels_1

# mob_indicators_1 <- mob_indicators_1 %>% 
  # mutate(new_jenk_class = str_replace(new_jenk_class, ",", "-"))

# change geometry
shp_reg <- region_shp %>% st_transform(crs = 'EPSG:4326')
```

```{r}
mob_indicators_1 <- na.omit(mob_indicators_1)
```


## Plotting

### Creating individual country map
```{r}

ggplot(data = mob_indicators_1, 
                           aes(fill = new_jenk_class )) +
  geom_sf(col = "white", size = .2) + 
  coord_sf() +
  scale_fill_brewer(palette = "OrRd", 
                    direction = 1, 
                    labels = c("< 32", "32-242", "243-1,640", "1641-30,291", "> 30,292"), 
                    na.value="black") +
  facet_grid(distance_class ~ year) +
  labs(title = "a Buenos Aires, Argentina",
       fill = "Number of out-moves") +
  theme_map() +
  guides(
    color='none',
    fill = guide_legend(
      keywidth = 3.2, 
      keyheight = 1,
      nrow = 1,
      title.position="top",
      label.position="bottom"
    )
  ) +
  theme(plot.title = element_text(size = 16, face = "bold"),
        plot.margin=margin(1,0,1,0,"cm"),
        legend.title = element_markdown(
          size=10, face = "bold", hjust=0.5, lineheight=0.45,
          color="black",
          margin=margin(0,0,-0.2,0,"cm")
          ),
        legend.text = element_text(size = 8),
        legend.position = "bottom",
        legend.spacing.x = unit(0, 'cm'),
        panel.background = element_rect(fill = "gray98", colour = "gray98")
        ) +
    geom_sf(data = shp_reg,
          col = "grey", 
          size = .5,
          fill = "transparent")

outflow_plot_arg <- last_plot()
```

### Saving map
```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/cloropleth-arg.png", units="in", width=8, height=10, res=300)
  outflow_plot_arg
dev.off()
```

# Chile

## Data

### mobility data
```{r}
## need to read this in 4 separate times - 202

# 2020 out
df20_b <- readRDS("/Volumes/RECAST/data/outputs/chile/movements/2020_04_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "CL") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')

# 2022 out
df22_b <- readRDS("/Volumes/RECAST/data/outputs/chile/movements/2022_03_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "CL") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')
```

### boundary data
```{r}
adm_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/Chile_shp/adm/province/PROVINCIAS_2020.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')

region_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/Chile_shp/adm/country/gadm41_CHL_0.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')
```

## Data wrangling
```{r}
df20_out <- df20_b %>% 
  filter(start_polygon_name == 'Santiago')
  
df22_out <- df22_b %>% 
  filter(start_polygon_name == 'Santiago')

```

### Define distance
```{r}
df20_out <- df20_out %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

df22_out <- df22_out %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

```

### preserve a unique geometry
```{r}
df20_out <- df20_out %>%
  group_by(end_polygon_name) %>%
  mutate(geometry = st_union(geometry)) %>%
  ungroup()

df22_out <- df22_out %>%
  group_by(end_polygon_name) %>%
  mutate(geometry = st_union(geometry)) %>%
  ungroup()
```

### Sum of flows
```{r}
outflows_df_20 <- df20_out %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, end_polygon_name, geometry, distance_class) %>% 
  dplyr::summarise(
    sum_outflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 

outflows_df_22 <- df22_out %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, end_polygon_name, geometry, distance_class) %>% 
  dplyr::summarise(
    sum_outflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 
```

### Check alignment between data frames
```{r}
p <- ggplot() + 
  geom_sf(data = adm_shp,
          color = "gray60", 
          size = 0.1) 

last_plot()
```

```{r}
p <- p +
  geom_point(data = outflows_df_20,
    aes(geometry = geometry),
    stat = "sf_coordinates"
  ) 
last_plot()
```

### Add year
```{r}
outflows_df_20$year <- '2020'
outflows_df_22$year <- '2022'
```

### Bind outflows
```{r}
outflows_df <- rbind(outflows_df_20, outflows_df_22)
```

### Join flows to polygons
```{r}
mob_indicators_1 <- st_join(adm_shp, outflows_df)
```

## classify data into quantiles
```{r}
mob_indicators_1$new_jenk_class <- classify_intervals(mob_indicators_1$sum_outflow, n = 5, style = "quantile", factor = TRUE)

outflow_labels_1 <- levels(mob_indicators_1$new_jenk_class)
outflow_labels_1 <- gsub("^.|.$", "",  outflow_labels_1)
outflow_labels_1 <- gsub("\\.[0-9]+", "",  outflow_labels_1)
outflow_labels_1 <- gsub("\\,", "-",  outflow_labels_1)
levels(mob_indicators_1$new_jenk_class) <- outflow_labels_1

# mob_indicators_1 <- mob_indicators_1 %>% 
  # mutate(new_jenk_class = str_replace(new_jenk_class, ",", "-"))

# change geometry
shp_reg <- region_shp %>% st_transform(crs = 'EPSG:4326')
```

```{r}
mob_indicators_1 <- na.omit(mob_indicators_1)
```


## Plotting

### Crop bounding box
```{r}
bbox_new <- st_bbox(adm_shp) # current bounding box

xrange <- bbox_new$xmax - bbox_new$xmin # range of x values
yrange <- bbox_new$ymax - bbox_new$ymin # range of y values

bbox_new[1] <- bbox_new[1] + (0.6 * xrange) # xmin - left

bbox_new <- bbox_new %>%  # take the bounding box ...
  st_as_sfc() # ... and make it a sf polygon

ggplot() + 
  geom_sf(data = adm_shp,
          color = "gray60", 
          size = 0.1) +
  geom_point(data = outflows_df_20,
    aes(geometry = geometry),
    stat = "sf_coordinates",
    size = .1
  ) +
  coord_sf(xlim = st_coordinates(bbox_new)[c(1,2),1], # min & max of x values
           ylim = st_coordinates(bbox_new)[c(2,3),2]) + # min & max of y values
  theme_void()
```

### Creating individual country map
```{r}

ggplot(data = mob_indicators_1, 
                           aes(fill = new_jenk_class )) +
  geom_sf(col = "white", size = .2) + 
  coord_sf() +
  scale_fill_brewer(palette = "OrRd", 
                    direction = 1, 
                    labels = c("< 421", "422-1231", "1,232-3,370", "3,371-22,761", "> 22,761"),
                    na.value="black") +
  facet_grid(distance_class ~ year) +
  labs(title = "b Santiago, Chile",
       fill = "Number of out-moves") +
  theme_map() +
  guides(
    color='none',
    fill=guide_legend(
      keywidth = 3.2, keyheight = 1,nrow = 1,
      title.position="top",label.position="bottom"
    )
  ) +
  theme(plot.title = element_text(size = 16, face = "bold"),
        plot.margin=margin(1,0,1,0,"cm"),
        legend.title = element_markdown(
          size=10, face = "bold", hjust=0.5, lineheight=0.45,
          color="black",
          margin=margin(0,0,-0.2,0,"cm")
          ),
        legend.text = element_text(size = 9),
        legend.position = "bottom",
        legend.spacing.x = unit(0, 'cm'),
        panel.background = element_rect(fill = "gray99", colour = "gray99")
        ) +
    geom_sf(data = region_shp,
          col = "grey", 
          size = .5,
          fill = "transparent") +
    coord_sf(xlim = st_coordinates(bbox_new)[c(1,2),1], 
           ylim = st_coordinates(bbox_new)[c(2,3),2]) 

outflow_plot_chi <- last_plot()
```
### Saving country map
```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/cloropleth-chi.png", units="in", width=8, height=10, res=300)
  last_plot()
dev.off()
```

# Mexico

### mobility data
```{r}
# 2020 out
df20_out <- readRDS("/Volumes/RECAST/data/outputs/mexico/movements/2020_04_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "MX") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')

# 2022 out
df22_out <- readRDS("/Volumes/RECAST/data/outputs/mexico/movements/2022_03_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "MX") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')
```

### boundary data
```{r}
# admin boundaries shape
adm_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_MEX_shp/gadm41_MEX_2.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')

# region shape
region_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_MEX_shp/gadm41_MEX_0.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')
```
## Data wrangling
```{r}
# filter for start location as mexico city
df20_out <- df20_out %>%
  filter(start_polygon_name == 'Ciudad De México')

df22_out <- df22_out %>%
  filter(start_polygon_name == 'Ciudad De México')

```

### Define distance
```{r}
df20_out <- df20_out %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

df22_out <- df22_out %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

```

### Sum of flows
```{r}
# sum of outflows
outflows_df_20 <- df20_out %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(geometry, distance_class) %>% 
  dplyr::summarise(
    sum_outflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 

outflows_df_22 <- df22_out %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(geometry, distance_class) %>% 
  dplyr::summarise(
    sum_outflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 

```
### Check alignment between data frames
```{r}
# plot boundaries - test 
p <- ggplot() + 
  geom_sf(data = adm_shp,
          color = "gray60", 
          size = 0.1) 

last_plot()
```

```{r}
# check geometry fits into either admin boundaries or region boundaries
p <- p +
  geom_point(data = outflows_df_20,
    aes(geometry = geometry),
    stat = "sf_coordinates"
  ) 
last_plot()
```
### Add year
```{r}
# assign a year to each
outflows_df_20$year <- '2020'
outflows_df_22$year <- '2022'
```

### Bind outflows
```{r}
outflows_df <- rbind(outflows_df_20, outflows_df_22)
```

### Join flows to polygons
```{r}
mob_indicators_1 <- st_join(adm_shp, outflows_df)
```

### classify data into quantiles
```{r}
mob_indicators_1$new_jenk_class <- classify_intervals(mob_indicators_1$sum_outflow, n = 5, style = "quantile", factor = TRUE)

outflow_labels_1 <- levels(mob_indicators_1$new_jenk_class)
outflow_labels_1 <- gsub("^.|.$", "",  outflow_labels_1)
outflow_labels_1 <- gsub("\\.[0-9]+", "",  outflow_labels_1)
outflow_labels_1 <- gsub("\\,", "-",  outflow_labels_1)
levels(mob_indicators_1$new_jenk_class) <- outflow_labels_1

# mob_indicators_1 <- mob_indicators_1 %>% 
  # mutate(new_jenk_class = str_replace(new_jenk_class, ",", "-"))

# change geometry
shp_reg <- region_shp %>% st_transform(crs = 'EPSG:4326')
```


```{r}
mob_indicators_1 <- na.omit(mob_indicators_1)
```


## Plotting

### Creating individual country map
```{r}

ggplot(data = mob_indicators_1, 
                           aes(fill = new_jenk_class )) +
  geom_sf(col = "white", size = .1) + 
  coord_sf() +
  scale_fill_brewer(palette = "OrRd", 
                    direction = 1, 
                    labels = c("< 92", "93-443", "444-1,654", "1,655-4,458", "> 3,221,210"), 
                    na.value="black") +
  facet_grid(distance_class ~ year) +
  labs(title = "c Mexico City, Mexico",
       fill = "Number of out-moves") +
  theme_map() +
  guides(
    color='none',
    fill = guide_legend(
      keywidth = 3.2, 
      keyheight = 1,
      nrow = 1,
      title.position="top",
      label.position="bottom"
    )
  ) +
  theme(plot.title = element_text(size = 16, face = "bold"),
        plot.margin = margin(1,0,1,0,"cm"),
        legend.title = element_markdown(
          size=10, face = "bold", hjust=0.5, lineheight=0.45,
          color="black",
          margin=margin(0,0,-0.2,0,"cm")
          ),
        legend.text = element_text(size = 8),
        legend.position = "bottom",
        legend.spacing.x = unit(0, 'cm'),
        panel.background = element_rect(fill = "gray99", colour = "gray99")
        ) +
    geom_sf(data = region_shp,
          col = "grey", 
          size = .5,
          fill = "transparent")

outflow_plot_mex <- last_plot()

```

### Saving country map
```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/cloropleth-mex1.png", units="in", width=8, height=10, res=300)
  outflow_plot_mex
dev.off()
```

### Saving combined maps
```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/cloropleth-map.png", units="in", width=8, height=10, res=300)
  outflow_plot_arg + outflow_plot_chi + outflow_plot_mex
dev.off()
```

```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/cloropleth-map1.png", units="in", width=8, height=10, res=300)
  plot_grid(outflow_plot_arg, outflow_plot_chi, outflow_plot_mex, ncol=3, align="h")
dev.off()
```





