---
title: "In-movement"
author: "F Rowe"
format: html
editor: visual
---

# Dependencies
```{r}
# data wrangling
library(tidyverse)

# spatial data wrangling
library(sf)

# data visualisation
library(viridis) 

# format data visualisations
library(ggthemes)
library(patchwork)
library(showtext)
library(scales)
library(classInt)
library(ggtext)

# create maps
library(leaflet)
library(tmap)
library(mapdeck)
library(patchwork)
library(cowplot)
```

# Setting theme

Set font style
```{r}
# clean workspace
rm(list=ls())
# load font
font_add_google("Roboto Condensed", "robotocondensed")
# automatically use showtext to render text
showtext_auto()
```

Theme for maps
```{r}
theme_map <- function(...) {
  theme_tufte() +
  theme(
    text = element_text(family = "robotocondensed", size = 25),
    # remove all axes
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
    )
}
```

Theme for plots

```{r}
theme_tufte2 <- function(...) {
  theme_tufte() +
  theme(
    text = element_text(family = "robotocondensed", size = 20),
    )
}

```

# Argentina

## Data

### mobility data
```{r}
## need to read this in 4 separate times - 202

# 2020 out
df20_a <- readRDS("/Volumes/RECAST/data/outputs/argentina/movements/2020_04_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "AR") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')

# 2022 out
df22_a <- readRDS("/Volumes/RECAST/data/outputs/argentina/movements/2022_03_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "AR") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')
```

### boundary data
```{r}
adm_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_ARG_shp/gadm41_ARG_2.shp") %>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')

adm1_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_ARG_shp/gadm41_ARG_1.shp") %>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')

region_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_ARG_shp/gadm41_ARG_0.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')
```


## Data wrangling
```{r}
area_names <- c("José C. Paz", "San Miguel", "Morón", "Capital Federal", "Esteban Echeverría", "Florencio Varela")

# filter for the area names which are within Buenos Aires
df20_in <- df20_a %>% dplyr::filter(end_polygon_name %in% area_names)
df22_in <- df22_a %>% dplyr::filter(end_polygon_name %in% area_names)

df20_in$end_polygon_name <- 'Buenos Aires'
df22_in$end_polygon_name <- 'Buenos Aires'

df20_in <- df20_in %>% filter(!start_polygon_name %in% area_names)
df22_in <- df22_in %>% filter(!start_polygon_name %in% area_names)
```

### Define distance
```{r}
df20_in <- df20_in %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

df22_in <- df22_in %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

```

### preserve a unique geometry
```{r}
df20_in <- df20_in %>%
  group_by(start_polygon_name) %>%
  mutate(geometry = st_union(geometry)) %>%
  ungroup()

df22_in <- df22_in %>%
  group_by(start_polygon_name) %>%
  mutate(geometry = st_union(geometry)) %>%
  ungroup()
```

### Sum of flows
```{r}
inflows_df_20 <- df20_in %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, end_polygon_name, geometry, distance_class) %>% 
  dplyr::summarise(
    sum_inflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 

inflows_df_22 <- df22_in %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, end_polygon_name, geometry, distance_class) %>% 
  dplyr::summarise(
    sum_inflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 
```
### Add year
```{r}
inflows_df_20$year <- '2020'
inflows_df_22$year <- '2022'
```

### Bind outflows
```{r}
inflows_df <- rbind(inflows_df_20, inflows_df_22)
```

### Join flows to polygons
```{r}
mob_indicators_1 <- st_join(adm_shp, inflows_df)
```


### classify data into quantiles
```{r}
mob_indicators_1$new_jenk_class <- classify_intervals(mob_indicators_1$sum_inflow, n = 5, style = "quantile", factor = TRUE)

inflow_labels_1 <- levels(mob_indicators_1$new_jenk_class)
inflow_labels_1 <- gsub("^.|.$", "",  inflow_labels_1)
inflow_labels_1 <- gsub("\\.[0-9]+", "",  inflow_labels_1)
inflow_labels_1 <- gsub("\\,", "-",  inflow_labels_1)
levels(mob_indicators_1$new_jenk_class) <- inflow_labels_1

# change geometry
shp_reg <- region_shp %>% st_transform(crs = 'EPSG:4326')
```

```{r}
mob_indicators_1$new_jenk_class <- mob_indicators_1$new_jenk_class %>% replace_na("10-219")
```

```{r}
mob_indicators_1 <- na.omit(mob_indicators_1)
```

## Plotting


### Creating individual country map
```{r}

ggplot(data = mob_indicators_1, 
                           aes(fill = new_jenk_class )) +
  geom_sf(col = "white", size = .2) + 
  coord_sf() +
  scale_fill_brewer(palette = "PuBu", 
                    direction = 1, 
                    labels = c("< 219", "219-1,178", "1,179-10,948", "10,949-66,413", "> 66,413"), 
                    na.value="black") +
  facet_grid(distance_class ~ year) +
  labs(title = "a Buenos Aires, Argentina",
       fill = "Number of in-moves") +
  theme_map() +
  guides(
    color='none',
    fill = guide_legend(
      keywidth = 2.5, 
      keyheight = 1,
      nrow = 1,
      title.position="top",
      label.position="bottom"
    )
  ) +
  theme(plot.title = element_text(size = 16, face = "bold"),
        plot.margin=margin(1,0,1,0,"cm"),
        legend.title = element_markdown(
          size=10, face = "bold", hjust=0.5, lineheight=0.45,
          color="black",
          margin=margin(0,0,-0.2,0,"cm")
          ),
        legend.text = element_text(size = 8),
        legend.position = "bottom",
        legend.spacing.x = unit(0, 'cm'),
        panel.background = element_rect(fill = "gray98", colour = "gray98")
        ) +
    geom_sf(data = shp_reg,
          col = "grey", 
          size = .5,
          fill = "transparent")

inflow_plot_arg <- last_plot()
```
### Saving map
```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/argentina/inflows-cloropleth-arg.png", units="in", width=8, height=10, res=300)
  inflow_plot_arg
dev.off()
```
### Create bar plot

```{r}
#try <- mob_indicators_1 %>% filter(year == "2022" & distance_class == ">100")
```



Long-distance
```{r}
col_pal <- c(#"#f1eef6",
             #"#bdc9e1",
             #"#74a9cf",
             "#2b8cbe",
             "#045a8d")

# 2020
mob_indicators_1 %>% filter(year == "2020") %>%
  filter(distance_class == ">100") %>% 
  distinct(start_polygon_name, new_jenk_class, .keep_all=TRUE) %>% 
  arrange(desc(sum_inflow)) %>% 
    mutate(inflow_total = sum(sum_inflow),
         inflow_percent = round( (sum_inflow/inflow_total)*100, 2 ) ) %>% 
  head(n = 10) %>% 
  ggplot(aes(x = reorder(start_polygon_name, inflow_percent), y = inflow_percent, fill = inflow_percent)) + 
  geom_bar(stat="identity" ) +     
  #scale_fill_manual(values= col_pal) +
   scale_fill_gradient2(
      low = "#f1eef6",  #2f2f5b
      mid = "#74a9cf", 
      high = "#045a8d", #6e191c
      midpoint = 0, 
      na.value = "grey90"
    ) +
  theme_tufte2() +
  coord_flip() +
  labs(title = "2020",
       y = "Percent (%)") +
  theme(plot.margin=margin(1,0,1,1,"cm"),
        legend.position = "none",
        plot.title = element_text(size = 30),
        axis.title.y = element_blank(),
       # axis.title.x = element_blank(),
        axis.ticks.y = element_blank()) # Set custom y-axis labels

in_barp_long2020 <- last_plot()
```


```{r}
# 2022
mob_indicators_1 %>% filter(year == "2022") %>%
  filter(distance_class == ">100") %>% 
  distinct(start_polygon_name, new_jenk_class, .keep_all=TRUE) %>% 
  arrange(desc(sum_inflow)) %>% 
    mutate(inflow_total = sum(sum_inflow),
         inflow_percent = round( (sum_inflow/inflow_total)*100, 2 ) ) %>% 
  head(n = 10) %>% 
  ggplot(aes(x = reorder(start_polygon_name, inflow_percent), y = inflow_percent, fill = inflow_percent)) + 
  geom_bar(stat="identity" ) + 
    scale_fill_brewer(palette = "PuBu", 
                    direction = 1, 
                    na.value="black") +
  #scale_fill_manual(values= col_pal) +
   scale_fill_gradient2(
      low = "#f1eef6",  #2f2f5b
      mid = "#74a9cf", 
      high = "#045a8d", #6e191c
      midpoint = 0, 
      na.value = "grey90"
    ) +
  theme_tufte2() +
  coord_flip() +
  labs(title = "Buenos Aires",
       y = "Percent (%)") +
  theme(plot.margin=margin(1,0,1,1,"cm"),
        legend.position = "none",
        plot.title = element_text(size = 30),
        axis.title.y = element_blank(),
       # axis.title.x = element_blank(),
        axis.ticks.y = element_blank()) # Set custom y-axis labels

ar_in_barp_long2022 <- last_plot()
```
```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/argentina/in-barp_long2020.png", units="in", width=8, height=10, res=300)
  in_barp_long2020
dev.off()

png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/argentina/in-barp_long2022.png", units="in", width=8, height=10, res=300)
  ar_in_barp_long2022
dev.off()
```
# Chile

## Data

### mobility data
```{r}
## need to read this in 4 separate times - 202

# 2020 out
df20_a <- readRDS("/Volumes/RECAST/data/outputs/chile/movements/2020_04_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "CL") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')

# 2022 out
df22_a <- readRDS("/Volumes/RECAST/data/outputs/chile/movements/2020_04_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "CL") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')
```

### boundary data
```{r}
adm_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/Chile_shp/adm/province/PROVINCIAS_2020.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')

region_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/Chile_shp/adm/country/gadm41_CHL_0.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')
```


## Data wrangling
```{r}
df20_in <- df20_a %>% 
  filter(end_polygon_name == 'Santiago')
  
df22_in <- df22_a %>% 
  filter(end_polygon_name == 'Santiago')

```

### Define distance
```{r}
df20_in <- df20_in %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

df22_in <- df22_in %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

```

### preserve a unique geometry
```{r}
df20_in <- df20_in %>%
  group_by(start_polygon_name) %>%
  mutate(geometry = st_union(geometry)) %>%
  ungroup()

df22_in <- df22_in %>%
  group_by(start_polygon_name) %>%
  mutate(geometry = st_union(geometry)) %>%
  ungroup()
```

### Sum of flows
```{r}
inflows_df_20 <- df20_in %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, geometry, distance_class) %>% 
  dplyr::summarise(
    sum_inflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 

inflows_df_22 <- df22_in %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, geometry, distance_class) %>% 
  dplyr::summarise(
    sum_inflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 
```
### Add year
```{r}
inflows_df_20$year <- '2020'
inflows_df_22$year <- '2022'
```

### Bind outflows
```{r}
inflows_df <- rbind(inflows_df_20, inflows_df_22)
```

### Join flows to polygons
```{r}
mob_indicators_1 <- st_join(adm_shp, inflows_df)
```


### classify data into quantiles
```{r}
mob_indicators_1$new_jenk_class <- classify_intervals(mob_indicators_1$sum_inflow, n = 5, style = "quantile", factor = TRUE)

inflow_labels_1 <- levels(mob_indicators_1$new_jenk_class)
inflow_labels_1 <- gsub("^.|.$", "",  inflow_labels_1)
inflow_labels_1 <- gsub("\\.[0-9]+", "",  inflow_labels_1)
inflow_labels_1 <- gsub("\\,", "-",  inflow_labels_1)
levels(mob_indicators_1$new_jenk_class) <- inflow_labels_1

# change geometry
shp_reg <- region_shp %>% st_transform(crs = 'EPSG:4326')
```

```{r}
mob_indicators_1$new_jenk_class <- mob_indicators_1$new_jenk_class %>% replace_na("10-69")
```

```{r}
mob_indicators_1 <- na.omit(mob_indicators_1)
```

## Plotting

### Creating bar graph
Long-distance
```{r}
col_pal <- c(#"#f1eef6",
             #"#bdc9e1",
             #"#74a9cf",
             "#2b8cbe",
             "#045a8d")

# 2020
mob_indicators_1 %>% filter(year == "2020") %>%
  filter(distance_class == ">100") %>% 
  distinct(start_polygon_name, new_jenk_class, .keep_all=TRUE) %>% 
  arrange(desc(sum_inflow)) %>% 
    mutate(inflow_total = sum(sum_inflow),
         inflow_percent = round( (sum_inflow/inflow_total)*100, 2 ) ) %>% 
  head(n = 10) %>% 
  ggplot(aes(x = reorder(start_polygon_name, inflow_percent), y = inflow_percent, fill = inflow_percent)) + 
  geom_bar(stat="identity" ) + 
  #scale_fill_manual(values= col_pal) +
   scale_fill_gradient2(
      low = "#f1eef6",  #2f2f5b
      mid = "#74a9cf", 
      high = "#045a8d", #6e191c
      midpoint = 0, 
      na.value = "grey90"
    ) +
  theme_tufte2() +
  coord_flip() +
  labs(title = "2020",
       y = "Percent (%)") +
  theme(plot.margin=margin(1,0,1,1,"cm"),
        legend.position = "none",
        plot.title = element_text(size = 30),
        axis.title.y = element_blank(),
       # axis.title.x = element_blank(),
        axis.ticks.y = element_blank()) # Set custom y-axis labels

in_barp_long2020 <- last_plot()

# 2022
mob_indicators_1 %>% filter(year == "2022") %>%
  filter(distance_class == ">100") %>% 
  distinct(start_polygon_name, new_jenk_class, .keep_all=TRUE) %>% 
  arrange(desc(sum_inflow)) %>% 
    mutate(inflow_total = sum(sum_inflow),
         inflow_percent = round( (sum_inflow/inflow_total)*100, 2 ) ) %>% 
  head(n = 10) %>% 
  ggplot(aes(x = reorder(start_polygon_name, inflow_percent), y = inflow_percent, fill = inflow_percent)) + 
  geom_bar(stat="identity" ) + 
  #scale_fill_manual(values= col_pal) +
   scale_fill_gradient2(
      low = "#f1eef6",  #2f2f5b
      mid = "#74a9cf", 
      high = "#045a8d", #6e191c
      midpoint = 0, 
      na.value = "grey90"
    ) +
  theme_tufte2() +
  coord_flip() +
  labs(title = "Santiago",
       y = "Percent (%)") +
  theme(plot.margin=margin(1,0,1,1,"cm"),
        legend.position = "none",
        plot.title = element_text(size = 30),
        axis.title.y = element_blank(),
       # axis.title.x = element_blank(),
        axis.ticks.y = element_blank()) # Set custom y-axis labels

cl_in_barp_long2022 <- last_plot()
```
```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/chile/in-barp_long2020.png", units="in", width=8, height=10, res=300)
  in_barp_long2020
dev.off()

png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/chile/in-barp_long2022.png", units="in", width=8, height=10, res=300)
  cl_in_barp_long2022
dev.off()
```

# Mexico

### mobility data
```{r}
# 2020
df20_in <- readRDS("/Volumes/RECAST/data/outputs/mexico/movements/2020_04_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "MX") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')

# 2022
df22_in <- readRDS("/Volumes/RECAST/data/outputs/mexico/movements/2022_03_mov.rds") %>% 
  mutate(GEOMETRY = NULL) %>% 
  dplyr::filter(country == "MX") %>% 
  st_as_sf(coords = c("end_lon", "end_lat"), 
                                      crs = 'EPSG:4326')
```

### boundary data
```{r}
# admin boundaries shape
adm_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_MEX_shp/gadm41_MEX_2.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')

adm1_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_MEX_shp/gadm41_MEX_1.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')

# region shape
region_shp <- st_read("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/data/maps/shapefiles/gadm41_MEX_shp/gadm41_MEX_0.shp")%>% 
  st_simplify(preserveTopology = T,
              dTolerance = 1000) %>% 
  st_make_valid() %>% 
  st_transform(crs = 'EPSG:4326')
```

## Data wrangling
```{r}
# filter for start location as mexico city
df20_in <- df20_in %>%
  filter(end_polygon_name == 'Ciudad De México')

df22_in <- df22_in %>%
  filter(end_polygon_name == 'Ciudad De México')

```

### Define distance
```{r}
df20_in <- df20_in %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

df22_in <- df22_in %>% mutate(
  distance_class = case_when(length_km < 100 ~ "<100",
                             length_km >= 100 ~ ">100"))

```

### Sum of flows
```{r}
# sum of outflows
inflows_df_20 <- df20_in %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, distance_class) %>% 
  dplyr::summarise(
    sum_inflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 

inflows_df_22 <- df22_in %>% 
  filter(start_polygon_name != end_polygon_name) %>% 
  group_by(start_polygon_name, distance_class) %>% 
  dplyr::summarise(
    sum_inflow = sum(n_crisis, na.rm = T)) %>% 
  ungroup() 

```

### Add year
```{r}
# assign a year to each
inflows_df_20$year <- '2020'
inflows_df_22$year <- '2022'
```


### Bind outflows
```{r}
inflows_df <- rbind(inflows_df_20, inflows_df_22)
```

### Join flows to polygons
```{r}
mob_indicators_1 <- st_join(adm_shp, inflows_df)
```

### classify data into quantiles
```{r}
mob_indicators_1$new_jenk_class <- classify_intervals(mob_indicators_1$sum_inflow, n = 5, style = "quantile", factor = TRUE)

inflow_labels_1 <- levels(mob_indicators_1$new_jenk_class)
inflow_labels_1 <- gsub("^.|.$", "",  inflow_labels_1)
inflow_labels_1 <- gsub("\\.[0-9]+", "",  inflow_labels_1)
inflow_labels_1 <- gsub("\\,", "-", inflow_labels_1)
levels(mob_indicators_1$new_jenk_class) <- inflow_labels_1

# mob_indicators_1 <- mob_indicators_1 %>% 
  # mutate(new_jenk_class = str_replace(new_jenk_class, ",", "-"))

# change geometry
shp_reg <- region_shp %>% st_transform(crs = 'EPSG:4326')
```


```{r}
mob_indicators_1 <- na.omit(mob_indicators_1)
```


## Plotting

### Creating bar graph

Long-distance

```{r}

# 2020
mob_indicators_1 %>% filter(year == "2020") %>%
  filter(distance_class == ">100") %>% 
  distinct(start_polygon_name, new_jenk_class, .keep_all=TRUE) %>% 
  arrange(desc(sum_inflow)) %>% 
    mutate(inflow_total = sum(sum_inflow),
         inflow_percent = round( (sum_inflow/inflow_total)*100, 2 ) ) %>% 
  head(n = 10) %>% 
  ggplot(aes(x = reorder(start_polygon_name, inflow_percent), y = inflow_percent, fill = inflow_percent)) + 
  geom_bar(stat="identity" ) + 
  #scale_fill_manual(values= col_pal) +
   scale_fill_gradient2(
      low = "#f1eef6",  #2f2f5b
      mid = "#74a9cf", 
      high = "#045a8d", #6e191c
      midpoint = 0, 
      na.value = "grey90"
    ) +
  theme_tufte2() +
  coord_flip() +
  labs(title = "2020",
       y = "Percent (%)") +
  theme(plot.margin=margin(1,0,1,1,"cm"),
        legend.position = "none",
        plot.title = element_text(size = 30),
        axis.title.y = element_blank(),
       # axis.title.x = element_blank(),
        axis.ticks.y = element_blank()) # Set custom y-axis labels

in_barp_long2020 <- last_plot()

# 2022
mob_indicators_1 %>% filter(year == "2022") %>%
  filter(distance_class == ">100") %>% 
  distinct(start_polygon_name, new_jenk_class, .keep_all=TRUE) %>% 
  arrange(desc(sum_inflow)) %>% 
    mutate(inflow_total = sum(sum_inflow),
         inflow_percent = round( (sum_inflow/inflow_total)*100, 2 ) ) %>% 
  head(n = 10) %>% 
  ggplot(aes(x = reorder(start_polygon_name, inflow_percent), y = inflow_percent, fill = inflow_percent)) + 
  geom_bar(stat="identity" ) + 
  #scale_fill_manual(values= col_pal) +
   scale_fill_gradient2(
      low = "#f1eef6",  #2f2f5b
      mid = "#74a9cf", 
      high = "#045a8d", #6e191c
      midpoint = 0, 
      na.value = "grey90"
    ) +
  theme_tufte2() +
  coord_flip() +
  labs(title = "Mexico City",
       y = "Percent (%)") +
  theme(plot.margin=margin(1,0,1,1,"cm"),
        legend.position = "none",
        plot.title = element_text(size = 30),
        axis.title.y = element_blank(),
       # axis.title.x = element_blank(),
        axis.ticks.y = element_blank()) # Set custom y-axis labels

mx_in_barp_long2022 <- last_plot()
```
```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/mexico/in-barp_long2020.png", units="in", width=8, height=10, res=300)
  in_barp_long2020
dev.off()

png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/mexico/in-barp_long2022.png", units="in", width=8, height=10, res=300)
  mx_in_barp_long2022 
dev.off()
```

```{r}
png("/Users/franciscorowe/Dropbox/Francisco/Research/in_progress/recast/cepal-report/outputs/cloropleth-maps/composite_in-barp_long2022.png", units="in", width=8, height=10, res=300)
  ar_in_barp_long2022 + cl_in_barp_long2022 + mx_in_barp_long2022 
dev.off()
```

